---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(reprex)
```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples. 

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`). 

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165

### Read in the data 

There are no problems here. 
```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 1: 
no
```

### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% 
  ggplot(aes(x = length1, y = weight)) +
         geom_point(shape = 12, color = "purple") +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
```

## End